Checkpoint 3

### 2020-04-23 Checkpoint3.Rmd
Update Checkpoint3.Rmd

Re-Cleaned 
```{r}
Finaldata <- Finaldata %>% select(-c(X))
```

@@

```{r}
## Creating a df of just the cases the week before 3/17
weekbefore <- data.frame(Finaldata) %>% filter(date <= as.Date("2020-03-17"))

@@

## Creating a df of just the cases the week after 3/17
weekafter <- data.frame(Finaldata) %>% filter(date >= as.Date("2020-03-17"))

>>>>

Re-Cleaned 
```{r}
Finaldata <- Finaldata %>% select(-c(X)) 
Finaldata <- Finaldata %>% mutate(as.Date(Day))
```

@@

```{r}
## Creating a df of just the cases the week before 3/17
weekbefore <- data.frame(Finaldata) %>% filter(Day <= as.character(as.Date("2020-03-17")))

@@

## Creating a df of just the cases the week after 3/17
weekafter <- data.frame(Finaldata) %>% filter(Day >= as.Date("2020-03-17"))
